\hypertarget{course-schedule}{%
\section{Course Schedule}\label{course-schedule}}

\textbf{Subject To Change}. Changes will be announced in class, through
email, and on the \href{https://lms.cofc.edu}{OAKS} course page.

\vspace{0.10in}

\noindent \textbf{All readings listed under \emph{Readings} below are
required}. Readings will be made available on
\href{https://lms.cofc.edu}{OAKS} and can be found under Content
-\textgreater{} Readings for each week.

\hypertarget{books}{%
\subsubsection{Books}\label{books}}

\begin{itemize}

\item
  \textbf{AJ}: Anderies, John M., and Marco A. Janssen. 2016.
  \emph{Sustaining the Commons}. Tempe, AZ: Center for Behavior,
  Institutions, and the Environment.
\item
  \textbf{Ostrom}: Ostrom, Elinor. 2005. \emph{Understanding
  Institutional Diversity}. Princeton, NJ: Princeton University Press.
\end{itemize}

\hypertarget{articles}{%
\subsubsection{Articles}\label{articles}}

You will be reading several peer-reviewed academic journal articles.
\emph{These will be made available as pdfs on}
\href{https://lms.cofc.edu}{OAKS}. In addition, you will be required to
find several journal articles on your own related to your research
project.

\hypertarget{links}{%
\subsubsection{Links}\label{links}}

I also provide several links to web based sources. You can access these
sources through the links on the syllabus or through
\href{https://lms.cofc.edu}{OAKS}.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\SetDate[16/08/2021]

\week \textbf{Course Introduction and Overview}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{SKIM} Cox, Michael. 2019. ``\emph{Using the Ostrom Workshop
    Frameworks to Study the Commons}.'' In Routledge Handbook of the
    Study of the Commons, Routledge Handbooks Online.
  \end{itemize}
\end{itemize}

\week \textbf{Common-Pool Resources}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{AJ}, Chapter 1: \emph{Why Study the Commons}?
  \item
    \href{https://blogs.scientificamerican.com/voices/the-tragedy-of-the-tragedy-of-the-commons/}{The
    Tragedy of the \emph{Tragedy of the Commons}}
  \item
    \textbf{SKIM}: Ostrom, Elinor. 2008. ``The Challenge of Common-Pool
    Resources.'' \emph{Environment: Science and Policy for Sustainable
    Development} 50(4): 8---21.
  \item
    Frischmann, Brett M., Alain Marciano, and Giovanni Battista Ramello.
    2019. ``Retrospectives: Tragedy of the Commons after 50 Years.''
    \emph{Journal of Economic Perspectives} 33(4): 211--28.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 1
  \end{itemize}
\end{itemize}

\week \textbf{Markets and Property Rights}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Keohane and Olmstead. 2016. ``The Efficiency of Markets'' in
    \emph{Markets and the Environment}
  \item
    Anderson, Terry L. and Gary D. Libecap. 2014. ``Property Rights for
    the Common Pool'' from \emph{Environmental Markets: A Property
    Rights Approach}
  \item
    Fullerton, Don, and Robert Stavins. 1998. ``How Economists See the
    Environment.'' \emph{Nature} 395(6701): 433---434.
  \item
    Anderson, Terry L. 2004. ``Donning Coase-Coloured Glasses: A
    Property Rights View of Natural Resource Economics.''
    \emph{Australian Journal of Agricultural and Resource Economics}
    48(3): 445---462.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 2
  \end{itemize}
\end{itemize}

\week \textbf{States and Regulation}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{SKIM}: Rowell, Arden, and Josephine van Zeben. 2021. \emph{A
    Guide to U.S. Environmental Law}. Oakland, California: University of
    California Press. \textbf{Part One: Building Blocks of U.S.
    Environmental Law}, pgs. 3-79
  \item
    Rowell and van Zeben, Chapter 7: \emph{Ecosystem Management}
  \item
    Pacheco-Vega, Raul. 2020. ``Environmental Regulation, Governance,
    and Policy Instruments, 20 Years After the Stick, Carrot, and Sermon
    Typology.'' \emph{Journal of Environmental Policy \& Planning}
    22(5): 620---635.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Research design part 1 DUE: Sept 15}
  \end{itemize}
\end{itemize}

\week \textbf{Institutions}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{AJ}, Chapter 2: \emph{Defining Institutions}
  \item
    \textbf{Ostrom}: Chapter 1, \emph{Understanding the Diversity of
    Structured Human Interactions}
  \item
    McGinnis, Michael D. 2011. ``An Introduction to IAD and the Language
    of the Ostrom Workshop: A Simple Guide to a Complex Framework.''
    \emph{Policy Studies Journal} 39(1): 169---183.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 3
  \end{itemize}
\end{itemize}

\week \textbf{Action Arenas}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{AJ}, Chapter 3: \emph{Action Arenas and Action Situations}
  \item
    \textbf{Ostrom}: Chapter 2, \emph{Zooming in and Linking Action
    Situations}
  \item
    McGinnis, Michael D. 2011. ``Networks of Adjacent Action Situations
    in Polycentric Governance.'' \emph{Policy Studies Journal} 39(1):
    51---78.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 4
  \end{itemize}
\end{itemize}

\week \textbf{Design Principles}

\begin{itemize}

\item
  \emph{Readings}

  \begin{itemize}
  
  \item
    \textbf{AJ}, Chapter 7: \emph{Design Principles to Sustain the
    Commons}
  \item
    Cox, Michael, Gwen Arnold, and Sergio Villamayor Tomas. 2010. ``A
    Review of Design Principles for Community-Based Natural Resource
    Management.'' \emph{Ecology and Society} 15(4).
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 5
  \end{itemize}
\end{itemize}

\week \textbf{Rules}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    AJ, Chapter 10: \emph{Classifying Rules}
  \item
    AJ, Chapter 11: \emph{Rules, Norms, and Shared Strategies}
  \item
    \textbf{SKIM} \textbf{Ostrom}: Chapter 5, \emph{A Grammar of
    Institutions}
  \item
    Siddiki, Saba et al.~2019. ``Institutional Analysis with the
    Institutional Grammar.'' \emph{Policy Studies Journal}, Forthcoming.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Research design part II DUE: Oct 13}
  \end{itemize}
\end{itemize}

\week \textbf{The Social-Ecological Systems Framework}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Ostrom, Elinor. 2009. ``A General Framework for Analyzing
    Sustainability of Social-Ecological Systems.'' \emph{Science}
    325(5939): 419---422.
  \item
    McGinnis, Michael, and Elinor Ostrom. 2014. ``Social-Ecological
    System Framework: Initial Changes and Continuing Challenges.''
    \emph{Ecology and Society} 19(2).
  \end{itemize}
\item
  \textbf{FALL BREAK: Oct 18-19}
\end{itemize}

\week \textbf{Systems}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    AJ, Chapter 12: \emph{Feedbacks and Stability}
  \item
    AJ, Chapter 13: \emph{Coupled Infrastructure Systems}
  \item
    Rammel, Christian, Sigrid Stagl, and Harald Wilfing. 2007.
    ``Managing Complex Adaptive Systems -- a Co-Evolutionary Perspective
    on Natural Resource Management.'' \emph{Ecological Economics} 63(1):
    9---21.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 6
  \end{itemize}
\end{itemize}

\week \textbf{Resilience of Social-Ecological Systems}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Folke, Carl. 2006. ``Resilience: The Emergence of a Perspective for
    Social-Ecological Systems Analyses.'' \emph{Global Environmental
    Change} 16(3): 253---267.
  \item
    Norberg, Jon, James Wilson, Brian Walker, and Elinor Ostrom. 2008.
    ``Diversity and Resilience of Social-Ecological Systems.'' In
    \emph{Complexity Theory for a Sustainable Future}, eds.~Jon Norberg
    and Graeme S. Cumming. New York, NY: Columbia University Press,
    46---79.
  \item
    Anderies, John M., and Marco A. Janssen. 2013. ``Robustness of
    Social-Ecological Systems: Implications for Public Policy.''
    \emph{Policy Studies Journal} 41(3): 513---536.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 7
  \end{itemize}
\end{itemize}

\week \textbf{Polycentricity}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    AJ, Chapter 14: \emph{Think Globally, Act Locally?}
  \item
    Ostrom, Elinor. 2010. ``Polycentric Systems for Coping with
    Collective Action and Global Environmental Change.'' \emph{Global
    Environmental Change} 20(4): 550---557.
  \item
    Lubell, Mark, and Matthew Robbins. 2021. ``Adapting to Sea-Level
    Rise: Centralization or Decentralization in Polycentric Governance
    Systems?'' \emph{Policy Studies Journal}, Forthcoming.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Research design part III DUE: Nov 10}
  \end{itemize}
\end{itemize}

\week \textbf{Polycentricity and the Ecology of Games}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Berardo, Ramiro, and Mark Lubell. 2019. ``The Ecology of Games as a
    Theory of Polycentricity: Recent Advances and Future Challenges.''
    \emph{Policy Studies Journal} 47(1): 6---26.
  \item
    Lubell, Mark. 2013. ``Governing Institutional Complexity: The
    Ecology of Games Framework.'' \emph{Policy Studies Journal} 41(3):
    537---559.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    Reflection paper 8
  \end{itemize}
\end{itemize}

\week \textbf{Conclusion}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Cox, Michael et al.~2021. ``Lessons Learned from Synthetic Research
    Projects Based on the Ostrom Workshop Frameworks.'' \emph{Ecology
    and Society} 26(1).
  \item
    Villamayor-Tomas, Sergio et al.~2020. ``Using Case Study Data to
    Understand SES Interactions: A Model-Centered Meta-Analysis of SES
    Framework Applications.'' \emph{Current Opinion in Environmental
    Sustainability} 44: 48---57.
  \end{itemize}
\item
  \textbf{THANKSGIVING BREAK: Nov 24-26}
\end{itemize}

\week \textbf{Presentations}

\week \textbf{Presentations}

\begin{itemize}

\item
  \textbf{Complete Research Design DUE: Dec 6}
\end{itemize}
